Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-06-09 revisionMemo/rev1.tex
additional sim cases

		We thank the reviewer for taking the time to provide these valuable comments. We have clarified our language in the paper (on page 1) to address this question.  Strategies like those employed by Aronow et al. do not directly model all relevant dependencies in the data but instead adjust the variance estimator. As Aronow et al. explain, "Of course, accounting for dynamic dyadic clustering may fail to fully account for all relevant dependencies in the data" (p. 16).   While such an approach decreases the risk of a type 1 error, it increases risk of type 2 error (if the mean estimate is biased downwards, increasing the variance estimate will lead us to falsely accept the null). The main aim of our research is to directly account for the relevant dependency structures in the data, thus providing an accurate estimate and addressing both types of possible errors.

@@

>>>>

		We thank the reviewer for taking the time to provide these valuable comments. We have clarified our language in the paper (on page 1) to address this question.  Strategies like those employed by Aronow et al. do not directly model all relevant dependencies in the data but instead adjust the variance estimator. As Aronow et al. explain, ``Of course, accounting for dynamic dyadic clustering may fail to fully account for all relevant dependencies in the data'' (p. 16).   While such an approach decreases the risk of a type 1 error, it increases risk of type 2 error (if the mean estimate is biased downwards, increasing the variance estimate will lead us to falsely accept the null). The main aim of our research is to directly account for the relevant dependency structures in the data, thus providing an accurate estimate and addressing both types of possible errors.

@@

		We've added additional discussion about how each of the variables in our simulation were generated.
